Development of a permanent magnet characterisation framework for use in low-field MRI systems

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

<br />
<p class="fragment">&#x2022; Expandable **open** datatypes for magnetic field data</p>
<br />
<p class="fragment">&#x2022; Prebuild analysis pipelines ready for user customisation</p>
<br />
<p class="fragment">&#x2022; Full online documentation, CI tested and user tutorials</p>

@@

<br />
<p class="fragment">&#x2022; Characterization of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and linearity</p>
<br />
<p class="fragment">&#x2022; Usage of the chrakterised sensor for sorting permanent magnets and measure magnetic fields</p>

@@

<aside class="notes">
* vereinfachter aufbau
* sensorplatte zeigen
* gleiche befdinungen
* zweites set an sensoren
</aside>

@@

<aside class="notes">
* TLV abweichung 0.2C (bitsprüunge) => nicht für temperatur compensation zu nutzen
* TLV mehr als doppelt so hoch wie im datenblatt (12bit 4096/260mT)
* Ergebnisse mit einem zweiten set an sensoren verifiziert
* MMC im noise weit unter datenblatt
</aside>

@@

### Manget Sorting

@@

#### Manget Sorting - DEMO MRP

@@

#### Manget Sorting - DEMO MRPCli

@@

#### Manget Sorting - DEMO MRPUdpp

@@

* The implemented framework was successfully used to automatically record and analyze measurement data
* Characterized sensors are only conditionally suitable for measuring low field MRI B0 fields
* Implementation of other sensor types required for a wider use of the implemented solution

>>>>

<br />
<p class="fragment">&#x2022; Expandable **open** data types for magnetic field data</p>
<br />
<p class="fragment">&#x2022; Prebuild analysis pipelines ready for user customisation</p>
<br />
<p class="fragment">&#x2022; Full online documentation,tests and user tutorials</p>

@@

<br />
<p class="fragment">&#x2022; Characterisation of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and linearity</p>
<br />
<p class="fragment">&#x2022; Usage of the chracterised sensor for sorting permanent magnets and measure magnetic fields</p>

@@

<aside class="notes">
* vereinfachter aufbau fuer alle gleich
* sensorplatte zeigen
* gleiche befdinungen
* zweites set an sensoren
</aside>

@@

<aside class="notes">
* aufgenommen weil
* TLV abweichung 0.2C (bitsprüunge) => nicht für temperatur compensation zu nutzen
* TLV mehr als doppelt so hoch wie im datenblatt (12bit 4096/260mT)
* Ergebnisse mit einem zweiten set an sensoren verifiziert
* MMC im noise weit unter datenblatt
</aside>

@@

### Magnet Sorting

@@

#### Magnet Sorting - DEMO MRP

@@

#### Magnet Sorting - DEMO MRPCli

@@

#### Magnet Sorting - DEMO MRPUdpp

@@

* The implemented framework is successfully used to automatically record and analyse measurement data
* Characterised sensors are only conditionally suitable for measuring low field MRI fields
* Implementation of other sensor types required for a wider use of the implemented solution
